Untitled

### 2022-09-28 code/0_preprocessing/0_preprocessingUS.Rmd
started new repo for manuscript

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("tidyjson")
library("gtools")
library("dplyr")
library(lme4)
library(digest)
library(lmerTest)
```
### Getting CN data
```{r import data, warning=FALSE, eval=F}
# read in raw data files
#folder_path = "~/Triad/data_expt/data_M/"
all_files <- list.files(path=folder_path, pattern="")

@@

cols_to_anon <- c("subject")
df$subject <- anonymise(df, cols_to_anon)

#write.csv(df, "data_anon0115_full.csv")

@@

df <- df_raw %>%
  mutate(responses = ifelse(responses == "锤子 ", "锤子", responses)) %>%
  mutate(top_opt = ifelse(top_opt == "锤子 ", "锤子", top_opt)) %>%
  mutate(bottom_opt = ifelse(bottom_opt == "锤子 ", "锤子", bottom_opt))

write.csv(df, "data_M_0530.csv")

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("tidyjson")
library("gtools")
library("dplyr")
library(lme4)
library(digest)
library(lmerTest)
```
### Getting US data
```{r import data, warning=FALSE, eval=F}
# read in all raw data files
#folder_path = "~/Triad/data_expt/data_E/"
all_files <- list.files(path=folder_path, pattern="")

@@

cols_to_anon <- c("subject")
df$subject <- anonymise(df, cols_to_anon)
```

df <- df_raw %>%
  mutate(responses = ifelse(responses == "hammer ", "hammer", responses)) %>%
  mutate(top_opt = ifelse(top_opt == "hammer ", "hammer", top_opt)) %>%
  mutate(bottom_opt = ifelse(bottom_opt == "hammer ", "hammer", bottom_opt))

write.csv(df, "data_E_0319.csv")

@@

### 2022-09-28 code/0_preprocessing/0_preprocessingVN.Rmd
started new repo for manuscript

---
title: "preprocessing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("tidyjson")
library("gtools")
library("dplyr")
library(lme4)
library(digest)
library(lmerTest)
```
### Getting US data
```{r import data, warning=FALSE, eval=F}
# read in all raw data files
#folder_path = "~/Triad/data_expt/data_E/"
all_files <- list.files(path=folder_path, pattern="")

@@

df <- df_raw %>%
  mutate(responses = ifelse(responses == "hammer ", "hammer", responses)) %>%
  mutate(top_opt = ifelse(top_opt == "hammer ", "hammer", top_opt)) %>%
  mutate(bottom_opt = ifelse(bottom_opt == "hammer ", "hammer", bottom_opt))

write.csv(df, "data_E_0319.csv")

```

>>>>

---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("tidyjson")
library("gtools")
library("dplyr")
library(lme4)
library(digest)
library(lmerTest)
```

### Getting VN data

```{r import data, warning=FALSE, eval=F}
# read in raw data files
#folder_path = "~/Triad/data_expt/data_V/"
all_files <- list.files(path=folder_path, pattern="")

@@

df <- df_raw %>%
  mutate(responses = ifelse(responses == "búa ", "búa", responses)) %>%
  mutate(top_opt = ifelse(top_opt == "búa ", "búa", top_opt)) %>%
  mutate(bottom_opt = ifelse(bottom_opt == "búa ", "búa", bottom_opt))

write.csv(df, "data_V_0530.csv")
```
